\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-04 papers/sbst22/paper_sbst22.tex
Update data in paper

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\TT}{{\sc T3}\xspace}

@@

%\input{macros}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{\EVOSUITE at the SBST 2021 Tool Competition}

\author{%
%
\IEEEauthorblockN{%
Sebastian Vogl\IEEEauthorrefmark{1}, 
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
Jose Campos\IEEEauthorrefmark{3},
and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

@@

\begin{abstract}
  \EVOSUITE is a search-based unit test generation tool for Java. This paper summarises the results and experiences of \EVOSUITE's participation at the ninth unit testing competition at SBST 2021, where \EVOSUITE achieved the highest overall score.
\end{abstract}

%------------------------------------------------------------------------- 
\section{Introduction}
%
The annual unit test generation competition aims to drive and evaluate progress
on unit test generation tools. Every year, a benchmark of Java classes is
selected, and different test generation tools are evaluated in terms of the
code coverage and mutation scores they can achieve on these classes. In the
2021 edition of the competition, six tools were applied on a set of 98 classes.
Details about the procedure of the competition, the technical framework, and
the benchmark classes can be found in the competition report~\cite{SBST:2021}.
\EVOSUITE achieved an overall score of 292.05, which was the highest among the
competing and baseline tools.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{CoverageBoxV}
	\vspace{-2em}
	\caption{\label{fig:results}Coverage results achieved in the competition.}
	\vspace{-1em}
\end{figure}

With an overall score of 292.05, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST:2021}, the score is calculated on the subset of 25 classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
mean coverage for the 25 classes used in the competition. While the coverage
increased from the 30 seconds to the 120 seconds search budget (mean line
coverage of 65.7\% vs. 77.1\%, respectively), the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). The likely
reason for this result is that \EVOSUITE crashed more frequently when given
more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
cases were generated. In most cases we found that the JVM process running
\EVOSUITE on the competition machine crashed with an
\texttt{OutOfMemoryException}, which possibly could have been avoided with a
more generous allocation of memory.

@@

A final observation is that all 25 Java classes considered in the competition
results were taken from the Guava project, which is notorious for its complex
use of Java Generics---which is a feature \EVOSUITE still struggles to handle
effectively. In particular, in 99 of all runs on the 25 competition classes
\EVOSUITE did not manage to move beyond the initial generation, which tends to
happen specifically when \EVOSUITE struggles to correctly instantiate complex,
nested generic types. This is currently a focus point of structural
improvements and refactorings in \EVOSUITE's codebase.

@@

This paper reports on the participation of the \EVOSUITE test generation tool
in the ninth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
search budget of 120 seconds on the 25 classes considered for the competition.
Overall, this results in a score of 292.05, which is the highest score of all
tools in the competition.

>>>>

\newcommand{\EVOSUITE}{\textsc{EvoSuite}\xspace}
\newcommand{\JTEXPERT}{\textsc{jTExpert}\xspace}
\newcommand{\RANDOOP}{\textsc{Randoop}\xspace}
\newcommand{\TT}{\textsc{T3}\xspace}

@@

\usepackage{siunitx}
\input{data/macros}

@@

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{\EVOSUITE at the SBST 2022 Tool Competition}

\author{%
%
\IEEEauthorblockN{%
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
Jose Campos\IEEEauthorrefmark{3},
and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

@@

\begin{abstract}
  \EVOSUITE is a search-based unit test generation tool for Java. This paper summarises the results and experiences of \EVOSUITE's participation at the 10th unit testing competition at SBST 2022, where \EVOSUITE achieved the highest overall score.
\end{abstract}

%------------------------------------------------------------------------- 
\section{Introduction}
%
The annual unit test generation competition aims to drive and evaluate progress
on unit test generation tools. Every year, a benchmark of Java classes is
selected, and different test generation tools are evaluated in terms of the
code coverage and mutation scores they can achieve on these classes. In the
2022 edition of the competition, seven tools were applied on a set of \cuts classes.
Details about the procedure of the competition, the technical framework, and
the benchmark classes can be found in the competition report~\cite{SBST-toolcomp22}.
\EVOSUITE achieved an overall score of \score, which was the highest among the
competing and baseline tools.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{data/CoverageBoxV}
	\vspace{-2em}
	\caption{\label{fig:results}Coverage results achieved in the competition.}
	\vspace{-1em}
\end{figure}

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition. While the coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively),
the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). The likely
reason for this result is that \EVOSUITE crashed more frequently when given
more time. For example, for 76 runs of \EVOSUITE on the \cuts classes no test
cases were generated. In most cases we found that the JVM process running
\EVOSUITE on the competition machine crashed with an
\texttt{OutOfMemoryException}, which possibly could have been avoided with a
more generous allocation of memory.

@@

A final observation is that all \cuts Java classes considered in the competition
results were taken from the Guava project, which is notorious for its complex
use of Java Generics---which is a feature \EVOSUITE still struggles to handle
effectively. In particular, in 99 of all runs on the \cuts competition classes
\EVOSUITE did not manage to move beyond the initial generation, which tends to
happen specifically when \EVOSUITE struggles to correctly instantiate complex,
nested generic types. This is currently a focus point of structural
improvements and refactorings in \EVOSUITE's codebase.

@@

This paper reports on the participation of the \EVOSUITE test generation tool
in the tenth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
\avgConditionsCoverageRatioLong branch coverage, \avgLinesCoverageRatioLong line coverage, 
and a mutation score of \avgMutantsCoverageRatioLong, using a
search budget of \budgetLong on the \cuts classes considered for the competition.
Overall, this results in a score of \score, which is the highest score of all
tools in the competition.
